Proposal full title \\ Proposal Acronym

### 2001-10-10 drafts/IST/PartB.tex
trivial fixes
svn path=/trunk/; revision=1523

%% DRAFT, be nice :-) . GM
The NAME project completely follows the \" Take up Action\" second objective.
Indeed, it is designed to allow anybody even with limited ressources to install
a development for free software. Therefore, even smallest projects will have a
complete platform which will use the generic interfaces available on bigger
sites. Furthermore, free software related organizations will have a complete
packaged solution to provide all the needed tools for development. Since the
project is completely distributed, it will have little architecture
requirements and then will be easy to integrate into an existing network.
\\ \\

@@

Current hosting plaforms are implemented as a  web site that provides
functionnalities to developpers. The most common ones include  users and groups
of users management, project repository (usualy based on Concurent Versionning
System), per project web pages and document sharing, per project mailing lists
and web forums, bugtracking system, project management system (audit, task
management), global site management and information feeding. There is currently
four main web hosting facilities : SourceForge (http://sourceforge.net/),
Savannah (http://savannah.gnu.org/), VHFFS (http://tuxfamily.org/), nd
Picolibre (http://picolibre.eu.org/). In terms of number of users and projects,
Savannah and SourceForge are the leaders.  \\

>>>>

%% DRAFT, be nice :-) . GM
The NAME project completely follows the '' Take up Action `` second objective.
Indeed, it is designed to allow anybody even with limited ressources to install
a development for free software. Therefore, even smallest projects will have a
complete platform which will use the generic interfaces available on bigger
sites. Furthermore, free software related organizations will have a complete
packaged solution to provide all the needed tools for development. Since the
project is completely distributed, it will have little architecture
requirements and then will be easy to integrate into an existing network.
\\ \\

@@

Current hosting plaforms are implemented as a  web site that provides
functionnalities to developpers. The most common ones include  users and groups
of users management, project repository (usualy based on Concurent Versionning
System), per project web pages and document sharing, per project mailing lists
and web forums, bugtracking system, project management system (audit, task
management), global site management and information feeding. There is currently
four main web hosting facilities : SourceForge (http://sourceforge.net/),
Savannah (http://savannah.gnu.org/), VHFFS (http://tuxfamily.org/), and
Picolibre (http://picolibre.eu.org/). In terms of number of users and projects,
Savannah and SourceForge are the leaders.  \\
